---
output:
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r, echo=FALSE, results='asis'}
bcgovr::insert_bcgov_devex_badge("Delivery")
```

# B.C. Roads in Raster Format
This analysis generates a raster spatial layer with the total length of roads per hectare for British Columbia. 

### Data

This analysis uses the British Columbia [Digital Road Atlas (DRA) available from the B.C. Data Catalogue]((https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e)) and distributed under the [Access Only - B.C. Crown Copyright ](https://www2.gov.bc.ca/gov/content?id=1AAACC9C65754E4D89A118B875E0FBDA) licence.

The Digital Road Atlas is the [best available single source of road data for the Province of B.C.](https://www2.gov.bc.ca/gov/content?id=21FFEC94B0AD40818D2D2AF06D522714) Metadata details for the Digital Road Atlas (DRA) are available in PDF format from the [B.C. Data Catalogue](https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e).

This analysis _excludes_ some surface and road types in the [Digital Road Atlas (DRA) ](https://catalogue.data.gov.bc.ca/dataset/bb060417-b6e6-4548-b837-f9060d94743e). Boat (B), overgrown (O) & decomissioned (D) roads are excluded from ```TRANSPORT_LINE_SURFACE_CODE``` and ferry routes (F, FP, FR, RWA), non-motorized trails (T, TD), road proposed (RP), and road pedestrian mall (RPM) are excluded from ```TRANSPORT_LINE_TYPE_CODE```.


### Usage

There are four core scripts that are required for the raster road density analysis, they need to be run in order:

- 01_load.R
- 02_clean.R
- 03_analysis.R
- 04_output.R

Or you can run all four scripts using run_all.R.

**Note about running time**: This is a large dataset and it takes 7-12 hours to complete.

The packages used in the analysis can be installed from CRAN using `install.packages()`.

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/bc-raster-roads/issues/).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

    Copyright 2017 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
    
This repository is maintained by [ENVEcosystems](https://github.com/orgs/bcgov/teams/envecosystems/members) and [Environmental Reporting BC](http://www2.gov.bc.ca/gov/content?id=FF80E0B985F245CEA62808414D78C41B). Click [here](https://github.com/bcgov/EnvReportBC-RepoList) for a complete list of Environmental Reporting BC repositories on GitHub. 
